\cvsection{Experience}
\begin{cventries}
 
  \cventry
    {Web Programmer}
    {Gravit Digital}
    {Bellingham, WA}
    {November 2017 - Present}
    {
      \begin{cvitems}
      \item {Script Programming}
      \item {Updates}
      \item {Writing Drupal Modules}
      \end{cvitems}
    }

  \cventry
    {System Administrator}
    {BizNex IT Management}
    {Bellingham, WA}
    {August 2017 - Present}
    {
      \begin{cvitems}
      \item {Break/Fix Issue Management}
      \item {Virus removal, clean-up, Windows management, Updates}
      \item {Updates for Windows, Windows Server, Software deployment}
      \end{cvitems}
    }

  \cventry
    {Replenishment Technician}
    {Kelly IT Services}
    {Bellingham, WA}
    {March 2016 - May 2016}
    {
      \begin{cvitems}
        \item {Laptop and Computer replacing, Dells specifically.}
        \item {Virus removal, clean-up, reinstallation of operating systems, and data recovery.}
        \item {Used Dell KACE tools for re-imaging and software deployment.}
      \end{cvitems}
    }

  \cventry
    {Computer Technician}
    {Blair’s Repair}
    {Bellingham, WA}
    {August 2014 - April 2016}
    {
      \begin{cvitems}
        \item {Laptop and Computer hardware repair, all makes and models.}
        \item {Virus removal, clean-up, reinstallation of operating systems, and data recovery.}
        \item {Windows 7 and 8 troubleshooting.  Mac OS troubleshooting.}
        \item {Troubleshooting and setup of Networks including Wireless systems.}
      \end{cvitems}
    }

  \cventry
    {Report Programmer}
    {St. Joseph Health}
    {Orange, CA}
    {March 2011 - November 2013}
    {
      \begin{cvitems}
        \item {Created and edited MEDITECH NPR Reports.}
        \item {Data extraction out of SQL to Excel.}
        \item {Created reports from SQL 2008 using SQL Server Reporting Services.}
        \item {Used HP/Unix for integration / messaging services running on Java.}
      \end{cvitems} 
    }
  \cventry
    {Computer Technician}
    {Blair’s Repair}
    {Bellingham, WA}
    {October 2009 - March 2011}
    {
      \begin{cvitems}
        \item {Laptop and Computer hardware repair, all makes and models. Virus removal, clean-up, reinstallation of operating systems, and data recovery. Setup ticketing system on CentOS Unix/Linux.}
      \end{cvitems}
    }
  \cventry
    {HL7/Interface Developer}
    {Allscripts-Misys}
    {South Burlington, VT}
    {March 2007 - May 2009}
    {
      \begin{cvitems}
        \item {HL7 and upgrading/customizing interfaces for Allscripts EMR with GE ConnectR.}
        \item {SQL 2005 and 2000.}
        \item {Wrote custom VBscript. Experience with developing a SharePoint site.}
        \item {Used excellent customer service skills.}
        \item {Experience with GE Imagelink.}
      \end{cvitems}
    }
  \cventry
    {UNIX Analyst}
    {Technical Connection}
    {Essex Junction, VT}
    {February 2005 - February 2007}
    {
      \begin{cvitems}
        \item {Worked at IBM Global Services on team supporting AIX and Linux servers running the manufacturing line. As part of a team of UNIX professionals I maintained, made system changes, installed upgrades, supported users, documented procedures, wrote scripts, and worked in various shells. I was on 24/7 support and I made sure all the computers ran as expected.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
\end{cventries}
